---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Sprintr

**sprintr** is a minimal R wrapper of the Jira and Jira Software REST APIs. 
Convienience functions with object parsing are available for retrieving sprint 
and velocity information. Bring the power of #rstats to your sprint reporting!

## Installation

`devtools::install_github("davidski/sprintr")`

The following environment variables must be set (typically via `.Renviron`)

| variable | purpose |
|----------|---------|
| JIRA_API_URL | endpoint of the Jira API (ex. https://yourdomain.atlassian.net) |
| JIRA_USER | username (ex. youraccount@example.com) |
| JIRA_API_KEY | API token obtained via [id.atlassian.net](https://id.atlassian.net) |

## Usage

Full docs are coming...

```{r example, eval = FALSE}
library(tidyverse)
library(sprintr)

# find the ID of the board of interest
get_boards() %>% head(1) %>% pull(id) -> my_board

# pull up details on a board
get_board_details(board_id = my_board)

# identify the sprint of interest
get_all_sprints(board_id = my_board) %>% arrange(desc(endDate)) %>% 
  head(1) %>% pull(id) -> my_sprint

# get a sprint report
sprint_report <- get_sprint_report(sprint_id = my_sprint)
# the report has quite a bit of info, for raw story point totals
sprint_report$points_sum

# pull up details on a specific issue
get_issue(issue_key = "XXX-1234")
# or see all the fields on that issue
get_issue("XXX-1234", full_response = TRUE)

# the main personal motivation of this package
sprint_report_detail <- get_sprint_report_detail(board_ud = my_board, sprint_id = my_sprint)
# do ggplot stuff!
```

## References

See the Atlassian [Jira Cloud](https://developer.atlassian.com/cloud/jira/platform/rest)
and [Jira Software Cloud](https://docs.atlassian.com/jira-software/REST/cloud) 
docuementation for more information.

## Contributing

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## License

The [MIT License](LICENSE) applies.
