---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Sprintr

**sprintr** is a minimal R wrapper of the Jira and Jira Software REST APIs. 
Convienience functions with object parsing are available for retrieving sprint 
and velocity information. Bring the power of #rstats to your sprint reporting!

## Installation

`devtools::install_github("davidski/sprintr")`

The following environment variables must be set (typically via `.Renviron`)

| variable | purpose |
|----------|---------|
| JIRA_API_URL | endpoint of the Jira API (ex. https//yourdomain.atlassian.net) |
| JIRA_USER | username (ex. youraccount@example.com) |
| JIRA_API_TOKEN | API token as set via id.atlassian.net |

## Usage

Full docs are coming...

```{r example, eval= FALSE}
# find the ID of the board of interst
get_boards()

# pull up details on a board
get_board_details(board_id = <x>)

# identify the sprint of interest
get_sprints(board_id = <x>) %>% arrange(desc(endDate))

# get a sprint report
sprint_report <- get_sprint_report(sprint_id = <x>)
# the report has quite a bit of info, for raw story point totals
sprint_report$points_sum

# pull up details on a specific issue
get_issue(issue_key = "XXX-1234")
# or see all the fields on that issue
get_issue("XXX-1234", full_response = TRUE)

# the main personal motivation of this package
sprint_report_detail <- get_sprint_report_detail(sprint_id = <x>)
# do ggplot stuff!
```

## Contributing

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## License

The [MIT License](LICENSE) applies.
