---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Sprintr

**sprintr** is a minimal R wrapper of the Jira and Jira Software REST APIs. 
Convienience functions with object parsing are available for retrieving sprint 
and velocity information. Bring the power of #rstats to your sprint reporting!

## Installation

`devtools::install_github("davidski/sprintr")`

Set the base url to your Jira API endpoint via the JIRA_API_URL environment 
variable (typically via `.Renviron`).

| variable | purpose |
|----------|---------|
| JIRA_API_URL | endpoint of the Jira API (ex. https://yourdomain.atlassian.net) |

### Atlassian Cloud Authentication

For Atlassian cloud installations, obtain a token via 
[id.atlassian.net](https://id.atlassian.net) and set the `JIRA_API_KEY` and 
`JIRA_USER` environment variables. 

| variable | purpose |
|----------|---------|
| JIRA_API_KEY | API token obtained via [id.atlassian.net](https://id.atlassian.net) |
| JIRA_USER | username (ex. youraccount@example.com) |
| JIRA_SESSION_COOKIE | Session authentication cookie

### Jira Server Authentication

While much of the Jira Server API is the same as the cloud endpoints, I've 
enountered many differences in practice and have not attempted to support them 
here in **sprintr**. If you wish to explore on your own (`jira_api()` 
and `jira_api_post()` both support making raw calls to the API) then proceed 
with the following kludgey  process to authenticate.

The **insecure** and **temporary** steps for authenticating to Jira Server are:

  1. Visit the `/rest/auth/1/session` endpoint and authenticate with basic 
  auth. (e.g. `curl -v --user YOURUID https://jira.yourdomain.tld/rest/auth1/session`)
  2. Copy out the JSESSIONID cookie value.
  3. Set an environment variable `JIRA_SESSION_COOKIE` to the value of the 
  JSESSION cookie, taking care to omit the `=` and the `;` that mark the respective 
  start and stop of the cookie value.
  
Session cookies will be preferred over API tokens, if available. Again, this is 
a very kludgey work around for Jira Servers which do not support OAuth.
  
| variable | purpose |
|----------|---------|
| JIRA_SESSION_COOKIE | Session authentication cookie

## Usage

Full docs are coming...

```{r example, eval = FALSE}
library(tidyverse)
library(sprintr)

# find the ID of the board of interest
get_boards() %>% head(1) %>% pull(id) -> my_board

# pull up details on a board
get_board_details(board_id = my_board)

# identify the sprint of interest
get_all_sprints(board_id = my_board) %>% arrange(desc(endDate)) %>% 
  head(1) %>% pull(id) -> my_sprint

# get a sprint report
sprint_report <- get_sprint_report(sprint_id = my_sprint)
# the report has quite a bit of info, for raw story point totals
sprint_report$points_sum

# pull up details on a specific issue
get_issue(issue_key = "XXX-1234")
# or see all the fields on that issue
get_issue("XXX-1234", full_response = TRUE)

# the main personal motivation of this package
sprint_report_detail <- get_sprint_report_detail(board_id = my_board, sprint_id = my_sprint)
# do ggplot stuff!
```

## References

See the Atlassian [Jira Cloud](https://developer.atlassian.com/cloud/jira/platform/rest)
and [Jira Software Cloud](https://docs.atlassian.com/jira-software/REST/cloud) 
docuementation for more information.

## Contributing

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## License

The [MIT License](LICENSE) applies.
