---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Sprintr

**sprintr** is a minimal R wrapper of the Jira and Jira Software REST APIs. 
Convenience functions with object parsing are available for retrieving sprint 
and velocity information. Bring the power of #rstats to your sprint reporting!

## Installation

`devtools::install_github("davidski/sprintr")`

Set the base url to your Jira API endpoint via the JIRA_API_URL environment 
variable (typically via `.Renviron`).

| variable | purpose |
|----------|---------|
| JIRA_API_URL | endpoint of the Jira API (ex. https://yourdomain.atlassian.net) |

### Atlassian Cloud Authentication

For Atlassian cloud installations, obtain a token via 
[id.atlassian.net](https://id.atlassian.net) and set the `JIRA_API_KEY` and 
`JIRA_USER` environment variables. 

| variable | purpose |
|----------|---------|
| JIRA_API_KEY | API token obtained via [id.atlassian.net](https://id.atlassian.net) |
| JIRA_USER | username (ex. youraccount@example.com) |

### Jira Server Authentication

My available versions of Jira Server do not support the same API as Jira Cloud. 
While **sprintr** aims for the lowest common denominator, there may be 
unexpected differences when 
operating on a Jira Server endpoint. Bug reports and PRs are very welcome!

To authenticate to Jira Server, you can use either use basic authentication 
or OAuth1.0 authentication. Basic authentication, while simpler, is **not recommended** 
and is provided only for local testing. Basic authentication will send your 
credentials unencrypted (apart from any HTTPS in use) across the network.

#### Basic Authentication

| variable | purpose |
|----------|---------|
| JIRA_USER | username (ex. youraccount@example.com) |
| JIRA_TOKEN | password |

#### OAuth1.0 Authentication

Jira's server edition uses signed OAuth 1.0 authentication. You, or your Jira 
server administrator, will need to create an OAuth endpoint. This endpoint 
should specify a return url of `http://localhost:1410`. As part of the setup 
process, your administrator will generate an OAuth consumer secret (short text string), a 
shared secret (short text string), and a private key (a long PEM-formatted key). 
The private key should be stored in a secure location on your installation of 
sprintr. Configure the following environment variables:

| variable | purpose |
|----------|---------|
| JIRA_USER | OAuth Consumer Secret |
| JIRA_API_KEY | Oauth Shared Secret |
| JIRA_OAUTH_SSL_KEY | full path to a PEM encoded private key |

## Usage

Full docs are coming...

```{r example, eval = FALSE}
library(tidyverse)
library(sprintr)

# find the Story Point field identifier for your environment
find_story_point_mapping()

# find the ID of the board of interest
get_boards() %>% head(1) %>% pull(id) -> my_board

# pull up details on a board
get_board_details(board_id = my_board)

# identify the sprint of interest
get_all_sprints(board_id = my_board) %>% arrange(desc(endDate)) %>% 
  head(1) %>% pull(id) -> my_sprint

# get a sprint report
sprint_report <- get_sprint_report(sprint_id = my_sprint)
# the report has quite a bit of info, for raw story point totals
sprint_report$points_sum

# pull up details on a specific issue
get_issue(issue_key = "XXX-1234")
# or see all the fields on that issue
get_issue("XXX-1234", full_response = TRUE)

# find all the epics associated with a board
get_epics(board_id = my_board)

# the main personal motivation of this package
sprint_report_detail <- get_sprint_report_detail(board_id = my_board, sprint_id = my_sprint)
# do ggplot stuff!
```

## References

See the Atlassian [Jira Cloud](https://developer.atlassian.com/cloud/jira/platform/rest)
and [Jira Software Cloud](https://docs.atlassian.com/jira-software/REST/cloud) 
documentation for more information.

## Contributing

Please note that this project is released with a 
[Contributor Code of Conduct](CONDUCT.md). By participating in this project you 
agree to abide by its terms.

## License

The [MIT License](LICENSE) applies.
